Your Title Goes Here

### 2017-12-29 documentation/documentation.tex
commiting the content of stata_analysis

\section{Data Analysis}
The data analysis was performed with the statistical software STATA. The corresponding stata file and .do file are stored in the folder statistical\_analysis\_stata. Following we describe all the commands used to produce our econometric model.

>>>>

\section{Data Analysis}
The data analysis was performed with the statistical software STATA (version 14.2). The corresponding stata file and .do file are stored in the folder stata\_analysis. Following we describe all the commands used to produce our econometric model.
